Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-10-20 psy_peds_3.Rmd
bootstrap added

>>>>

### ITS bootstrap

```{r, eval=FALSE}
### list to save the bootstrap results 
list_results <- list()
list_predict_results <- list()
number_of_iterations <- 1000

set.seed( seed = 1 )

for( i in 1:number_of_iterations){
#  print(i)
  sample_size = nrow(all_codes_desc)
  sample_size
  row_indices <- 1:nrow(all_codes_desc)

  sample_df <- all_codes_desc[sample(row_indices, size = sample_size, replace = TRUE),]
  dim(sample_df)

  sample_df_psy <- sample_df %>% 
    filter(concept_code %in% icdCodes$ICD10_Code)

  all_patients_bootstrap <- unique( sample_df[, c("patient_num", "time_p")])
  patients_with_psy_conditions_bootstrap <- unique( sample_df_psy[, c("patient_num", "time_p")] )
  patients_without_psy_conditions_bootstrap <- setdiff(all_patients_bootstrap,patients_with_psy_conditions_bootstrap)

  patients_without_psy_conditions_counts_bootstrap <- patients_without_psy_conditions_bootstrap %>%
    group_by( time_p ) %>%
    summarise(count_no_psy_patients =  ifelse(n_distinct(patient_num) > obfuscation | isFALSE(obfuscation),
                                              n_distinct(patient_num), 
                                              0.5)) %>%
    mutate( period = ifelse( time_p < pandemic_start_date,
                             "before_pandemic",
                             "during_pandemic"))

  patients_with_psy_conditions_counts_bootstrap <-  patients_with_psy_conditions_bootstrap %>%
    group_by( time_p ) %>%
    summarise(count_psy_patients =  ifelse(n_distinct(patient_num) > obfuscation | isFALSE(obfuscation),
                                           n_distinct(patient_num), 
                                           0.5)) %>%
    mutate( period = ifelse( time_p < pandemic_start_date,
                             "before_pandemic",
                             "during_pandemic"))

  ratios_patients_with_without_psy_bootstrap <- patients_without_psy_conditions_counts_bootstrap %>%
    full_join( patients_with_psy_conditions_counts_bootstrap, by=c("time_p", "period")) %>%
    mutate( ratio = count_psy_patients/count_no_psy_patients, 
            percentage = 100 * count_psy_patients/(count_no_psy_patients + count_psy_patients))

  patient_count_psy_period_psy_bootstrap <- ratios_patients_with_without_psy_bootstrap %>%
    filter(time_p > as.Date(cut( start_date_plots, breaks = time_period)) &
             time_p < as.Date(cut( end_date_plots, breaks = time_period))) %>%
    mutate(time = seq_along(time_p),
           month_year = format(time_p, "%m")
    )

  ts_linear_percent_bootstrap <- lm(percentage ~ period * time, patient_count_psy_period_psy_bootstrap)
  output_model_bootstrap <- broom::tidy( ts_linear_percent_bootstrap )
  bootstrap_results <- output_model_bootstrap["estimate"]
  list_results[[i]] <- bootstrap_results

  pred_model_bootstrap <- predict(ts_linear_percent_bootstrap, patient_count_psy_period_psy_bootstrap, type = "response") %>% as.data.frame()
  pred_model_bootstrap <- bind_cols(patient_count_psy_period_psy_bootstrap, pred_model_bootstrap)
  list_predict_results[[i]] <- pred_model_bootstrap

}
```

```{r }
load("../ooutput_bootsrap1000iterations.RData")
load("../output_bootstrap_predict_results1000iterations.RData")

ggplot(data = output_bootstrap_predict_results, aes(x = time_p, 
                                                    y = fittedValue)) + 
  geom_line(aes(group = iteration,
                color = period), 
            data = output_bootstrap_predict_results[output_bootstrap_predict_results$period == "before_pandemic", ], 
            alpha = 0.05) +
  geom_line(aes(group = iteration,
                color = period), 
            data = output_bootstrap_predict_results[output_bootstrap_predict_results$period == "during_pandemic", ], 
            alpha = 0.05) +
  geom_smooth(formula = y ~ x, data = output_bootstrap_predict_results[output_bootstrap_predict_results$period == "during_pandemic", ], 
              color = "black") +
  geom_smooth(formula = y ~ x, data = output_bootstrap_predict_results[output_bootstrap_predict_results$period == "before_pandemic", ], 
              color = "black")
```

```{r }
